ms_figures

### 2018-01-24 man/ms_tables/t_sampled_plots.Rmd
update sampled plots

**Table 1.** Characteristics of sampled plot. Lat = latitude; Long = longitude. Dbh and height of all trees, Basal Area (BA) and Density are computed for all trees within a 10-m radius of focal trees (see methods). Values shown here correspond to site averages. Standard deviations are shown in parentheses. Different letters indicate statistically significant differences between sites (Kruskal-Wallis test followed by Dunn’s test, p<0.05).

@@

t1 <- t1raw %>% dplyr::select(
  site, lat_m, long_m, elev_mean, slope_mean, 
  n_trees, n_radii, dn_mean, dn_sd, h_mean, h_sd, age_mean, age_std, 
  dn_mean_all, dn_sd_all, h_mean_all, h_sd_all,
  ba_mean, ba_sd, stand_density_mean, stand_density_sd, 
  all_dn_l, all_h_l, ba_l, ft_dn_l, ft_h_l, std_l
  ) %>% 
  mutate(pare = ")") %>% 
  mutate_at(c(2,3,5,18,19), round, 2) %>% 
  mutate_at(4, round, 0) %>% 
  mutate_at(c(8:17, 20:21), round, 1) %>% 
  unite(dn, c(dn_mean, dn_sd), sep=" (") %>% 
  unite(h, c(h_mean, h_sd), sep=" (") %>% 
  unite(age, c(age_mean, age_std), sep=" (") %>% 
  unite(dn_all, c(dn_mean_all, dn_sd_all), sep=" (") %>% 
  unite(h_all, c(h_mean_all, h_sd_all), sep=" (") %>% 
  unite(ba, c(ba_mean, ba_sd), sep=" (") %>% 
  unite(stand_density, c(stand_density_mean, stand_density_sd), sep=" (") %>% 
  mutate(
    dn = paste(paste0(dn, pare), ft_dn_l, sep=" "),
    h = paste(paste0(h, pare), ft_h_l, sep = ' '),
    age = paste0(age, pare),
    dn_all = paste(paste0(dn_all, pare), all_dn_l, sep = ' '),
    h_all = paste(paste0(h_all, pare), all_h_l, sep = ' '),
    ba = paste(paste0(ba, pare), ba_l, sep = ' '),
    stand_density = paste(paste0(stand_density, pare), std_l, sep = ' ')) %>%
  dplyr::select(-pare, -all_dn_l, -all_h_l, -ba_l, -ft_dn_l, -ft_h_l, -std_l)

colnames (t1) <- c("Site", "Lat (&deg;)", "Long (&deg;)", "Elevation (m)", "Slope (&deg;)", 
                   "# trees", '# cores', "Dbh (cm)", "Height (m)", "Age (years)", 
                   "Dbh all (cm)", "Height all (m)", "BA (m2/ha)", "Density (trees/ha)")

>>>>

**Table 1.** Characteristics of sampled plot. Lat = latitude; Long = longitude. Dbh and height of all trees, Basal Area (BA), Density and SRD (Size ratio proportional to distance) are computed for all trees within a 10-m radius of focal trees (see methods). Values shown here correspond to site averages. Standard deviations are shown in parentheses. Different letters indicate statistically significant differences between sites (Kruskal-Wallis test followed by Dunn’s test, p<0.05).

@@

t1 <- t1raw %>% dplyr::select(
  site, lat_m, long_m, elev_mean, slope_mean, 
  n_trees, n_radii, dn_mean, dn_sd, h_mean, h_sd, age_mean, age_std, 
  dn_mean_all, dn_sd_all, h_mean_all, h_sd_all,
  ba_mean, ba_sd, stand_density_mean, stand_density_sd, srd_mean, srd_sd,
  all_dn_l, all_h_l, ba_l, ft_dn_l, ft_h_l, std_l, srd_l
  ) %>% 
  mutate(pare = ")") %>% 
  mutate_at(c(2,3,5,18,19, 22:23), round, 2) %>% 
  mutate_at(4, round, 0) %>% 
  mutate_at(c(8:17, 20:21), round, 1) %>% 
  unite(n_trees, c(n_trees, n_radii), sep=" (") %>% 
  unite(dn, c(dn_mean, dn_sd), sep=" (") %>% 
  unite(h, c(h_mean, h_sd), sep=" (") %>% 
  unite(age, c(age_mean, age_std), sep=" (") %>% 
  unite(dn_all, c(dn_mean_all, dn_sd_all), sep=" (") %>% 
  unite(h_all, c(h_mean_all, h_sd_all), sep=" (") %>% 
  unite(ba, c(ba_mean, ba_sd), sep=" (") %>% 
  unite(stand_density, c(stand_density_mean, stand_density_sd), sep=" (") %>% 
  unite(srd, c(srd_mean, srd_sd), sep=" (") %>% 
  mutate(
    n_trees = paste0(n_trees, pare),
    dn = paste(paste0(dn, pare), ft_dn_l, sep=" "),
    h = paste(paste0(h, pare), ft_h_l, sep = ' '),
    age = paste0(age, pare),
    dn_all = paste(paste0(dn_all, pare), all_dn_l, sep = ' '),
    h_all = paste(paste0(h_all, pare), all_h_l, sep = ' '),
    ba = paste(paste0(ba, pare), ba_l, sep = ' '),
    stand_density = paste(paste0(stand_density, pare), std_l, sep = ' '),
    srd = paste(paste0(srd, pare), srd_l, sep = ' ')) %>%
  dplyr::select(-pare, -all_dn_l, -all_h_l, -ba_l, -ft_dn_l, -ft_h_l, -std_l, -srd_l)

colnames (t1) <- c("Site", "Lat (&deg;)", "Long (&deg;)", "Elevation (m)", "Slope (&deg;)", 
                   "# trees (# cores)", "Dbh (cm)", "Height (m)", "Age (years)", 
                   "Dbh all (cm)", "Height all (m)", "BA (m2/ha)", "Density (trees/ha)", "SRD")
